---
title: "MAS8404 Practical Report 2"
author: "Mansoor Hamid"
date: "11/9/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```
### Question 1:

#### Part(a)
```{r}
genexpr_data=read.csv("C:/Users/User/Documents/RWorkSpace/data/Ch10Ex11.csv",header=TRUE)
#Check dimesion of the loaded data
dim(genexpr_data)

#transpose once to correct the data
genexpr_data = t(genexpr_data)
```
##### Creating correlation distance matrix
```{r}
#Transpose the matrix in order to use cor function
genexpr_data_transposed = t(genexpr_data)

#Compute the inter-observation correlations
r_obs = cor(genexpr_data_transposed)
#Create the distance matrix
d_cor = 1-r_obs

#convert the distance matrix to dis object
d_cor = as.dist(d_cor)
```
##### Perform hierarchical clustering using hclust with metod specified as "single" to indicate single-linkage
```{r}
hc_c = hclust(d_cor, method = "single")
```
##### Plot the dendrogram
```{r}
plot(hc_c, cex=0.5,main="",sub="",xlab="")
```

#### Part(b)

##### Perform hierarchical clustering using hclust with metod specified as "complete" and "average"
```{r}
hc_c_complete = hclust(d_cor, method = "complete")
hc_c_average = hclust(d_cor, method = "average")
```
##### Plot the dendrograms
```{r}
plot(hc_c_complete, cex=0.5,main="",sub="",xlab="")
plot(hc_c_average, cex=0.5,main="",sub="",xlab="")
```

#### Part(c)

###### Determine Euclidean distance and perform hierarchical clustering with single-linkage 
```{r}
genexpr_data_euc = dist(genexpr_data)
hc_c_euc_single = hclust(genexpr_data_euc, method = "single")
```
##### Plot the dendrogram
```{r}
plot(hc_c_euc_single, cex=0.5,main="",sub="",xlab="")
```

### Question 2:

#### Part(a)
```{r}
#Scale the data
Kmax = 10
genexpr_data_scaled = scale(genexpr_data)


```